---
title: "P8015_Hw1_agd2159"
output: github_document
author: "Zander De Jesus"
date: "09-23-2023"
---

## Problem 1: Inline R Code and Using GGplot
```{r, include= FALSE}
#install.packages("moderndive")
```

Beginning by importing required libraries:
```{r}
library(tidyverse)
library(moderndive)
```

Importing Weather Sample Dataset from Moderndive and initial summary statistics:
```{r}
data("early_january_weather")
weather_df = early_january_weather
weather_df

#Identified Important Variables in this Tibble after observing using these functions:
#view(weather_df)
summary(weather_df)
nrow(weather_df) 
ncol(weather_df)
mean(pull(weather_df, "temp"))
```

### Prob. 1 Dataframe Summary 
This imported dataset, named **weather_df** in this exercise, is a tibble dataframe that contains the first 15 days of weather readings from January 2013. 
Data points for important weather metrics were recorded on an hourly basis. When evaluated with nrow and ncol, the dataframe contains `r nrow(weather_df)` rows and `r ncol(weather_df)` columns.

* Weather Variables Measured in this Dataframe include:
  * **Temperature** in Degrees Fahrenheit. The mean temperature across these days was **`r mean(pull(weather_df, "temp"))` Degrees**. 
  * **Dewpoint**, which had a mean of `r mean(pull(weather_df, "dewp"))` and standard deviation of `r sd(pull(weather_df, "dewp"))`.
  * **Relative Humidity**, with a mean of `r mean(pull(weather_df, "humid"))` and standard deviation of `r sd(pull(weather_df, "humid"))`.
  * **Wind Direction** in degrees from true north. Mean 208.2 degrees.
  * **Wind Speed**. Mean of `r mean(pull(weather_df, "wind_speed"))` and standard deviation of `r sd(pull(weather_df, "wind_speed"))`.
  * **Wind Gust**, not measured for most entries. Mean 22.53.
  * **Precipitation**. Mean of `r mean(pull(weather_df, "precip"))` and standard deviation of `r sd(pull(weather_df, "precip"))`.
  * **Atmospheric Pressure** measured in pascals. Mean of 1023 Pa.
  * **Visibility**. Mean of `r mean(pull(weather_df, "visib"))` and `r sd(pull(weather_df, "visib"))`.
  * Exact Time Stamps by Hour.
  
### Prob. 1 Scatterplot Generation

```{r}
#Define Variables 
Time_Hour = pull(weather_df, "time_hour")
Temp = pull(weather_df, "temp")
Humidity = pull(weather_df, "humid")

ggplot(weather_df, aes(x= Time_Hour, y = Temp, color = Humidity)) + geom_point()
ggsave("ScatterplotFirstDraft.pdf")

```




