---
title: "P8015_Hw1_agd2159"
output: github_document
author: "Zander De Jesus"
date: "09-23-2023"
---

## Problem 1: Inline R Code and Using GGplot
```{r, include= FALSE}
#install.packages("moderndive")
```

Beginning by importing required libraries:
```{r}
library(tidyverse)
library(moderndive)
```

Importing Weather Sample Dataset from Moderndive and initial summary statistics:
```{r}
data("early_january_weather")
weather_df = early_january_weather
weather_df

#Identified Important Variables in this Tibble after observing using these functions:
#view(weather_df)
summary(weather_df)
nrow(weather_df) 
ncol(weather_df)
mean(pull(weather_df, "temp"))
drop_na(weather_df)
```

### P1 Dataframe Summary 
This imported dataset, named **weather_df** in this exercise, is a tibble dataframe that contains the first 15 days of weather readings from January 2013. 
Data points for important weather metrics were recorded on an hourly basis. When evaluated with nrow and ncol, the dataframe contains `r nrow(weather_df)` rows and `r ncol(weather_df)` columns.

* Weather Variables Measured in this Dataframe include:
  * Temperature in Degrees Fahrenheit. The mean temperature across these days was **`r mean(pull(weather_df, "temp"))` Degrees**. 
  * Dewpoint, which had a mean of `r mean(pull(weather_df, "dewp"))` and standard deviation of `r sd(pull(weather_df, "dewp"))`
  * Relative Humidity, with a mean of `r mean(pull(weather_df, "humid"))` and standard deviation of `r sd(pull(weather_df, "humid"))`
  * Wind Direction in degrees from true north
  * Wind Speed. Mean of `r mean(pull(weather_df, "wind_speed"))` and standard deviation of `r sd(pull(weather_df, "wind_speed"))`
  * Wind Gust, not measured for most entries.
  * Precipitation. Mean of `r mean(pull(weather_df, "precip"))` and standard deviation of `r sd(pull(weather_df, "precip"))`
  * Visibility
  * Exact Time Stamps by Hour
  

