---
title: "P8015_Hw1_agd2159"
output: github_document
author: "Zander De Jesus"
date: "09-23-2023"
---

## Problem 1: Inline R Code and Using GGplot

Beginning by importing required libraries:
```{r}
library(tidyverse)
library(moderndive)
```

Importing Weather Sample Dataset from Moderndive and initial summary statistics:
```{r Creating Dataframe}
data("early_january_weather")
weather_df = early_january_weather
weather_df

#Identified Important Variables in this Tibble after observing using these functions:
#view(weather_df)
summary(weather_df)
nrow(weather_df) 
ncol(weather_df)
mean(pull(weather_df, "temp"))
```

### Prob. 1 Dataframe Summary 
This imported dataset, named **weather_df** in this exercise, is a tibble dataframe that contains the first 15 days of weather readings from January 2013. 
Data points for important weather metrics were recorded on an hourly basis. When evaluated with nrow and ncol, the dataframe contains `r nrow(weather_df)` rows and `r ncol(weather_df)` columns.

* Weather Variables Measured in this Dataframe include:
  * **Temperature** in Degrees Fahrenheit. The mean temperature across these days was **`r mean(pull(weather_df, "temp"))` Degrees**. 
  * **Dewpoint**, which had a mean of `r mean(pull(weather_df, "dewp"))` and standard deviation of `r sd(pull(weather_df, "dewp"))`.
  * **Relative Humidity**, with a mean of `r mean(pull(weather_df, "humid"))` and standard deviation of `r sd(pull(weather_df, "humid"))`.
  * **Wind Direction** in degrees from true north. Mean 208.2 degrees.
  * **Wind Speed**. Mean of `r mean(pull(weather_df, "wind_speed"))` and standard deviation of `r sd(pull(weather_df, "wind_speed"))`.
  * **Wind Gust**, not measured for most entries. Mean 22.53.
  * **Precipitation**. Mean of `r mean(pull(weather_df, "precip"))` and standard deviation of `r sd(pull(weather_df, "precip"))`.
  * **Atmospheric Pressure** measured in pascals. Mean of 1023 Pa.
  * **Visibility**. Mean of `r mean(pull(weather_df, "visib"))` and `r sd(pull(weather_df, "visib"))`.
  * Exact Time Stamps by Hour.
  
### Prob. 1 Scatterplot Generation

```{r Weather Scatterplot}
#Define Variables 
Time_Hour = pull(weather_df, "time_hour")
Temp = pull(weather_df, "temp")
Humidity = pull(weather_df, "humid")

ggplot(weather_df, aes(x= Time_Hour, y = Temp, color = Humidity)) + geom_point()
ggsave("ScatterplotFirstDraft.pdf")

```

The Scatterplot above visualizes the hourly temperature readings recorded across this 15 day period in January, with each point colored by its respective humidity readings. The lighter the blue, the higher the humidity.

From this Scatterplot we can see that there is a visible day-night cycle visualized, where temperature dips down during the night hours and rises higher over the next day. Across the week, the temperature appears to rise from day to day, with January 1 and 2 having average temperatures between 30 and 40 degrees and the middle of the week around January 7 rising into the 50 degrees. Near the end of the measurement period, there is the largest temperature increase from January 12-14 where the temperature rises from the mid 40s into the mid 50s. The Humidity appears to be highest from January 12 - 14 as well. By January 15, the temperature drops back down to low 40s high 30 degrees. 




# Problem 2: Generating Random Dataframe and Manipulating Variables

```{r Random Dataframe}
set.seed(1234)

prob2_df = 
  tibble(
    num_sample = rnorm(10),
    log_vec = num_sample > 0,
    char_vec = c("A", "B", "C", "D", "E", "AA", "BB", "CC", "DD", "EE"),
    factor_vec = factor(c("lemon", "lemon", "lemon", "mango","mango","mango","mango","apple", "apple", "apple"), levels = c("lemon", "mango", "apple"))
  )

prob2_df

```

First attempt to calculate the means of these generated dataframe columns using the pull function, only allows the `num_sample` and `log_vec` columns to be calculated, because the "dbl" and "lgl" data types are considered numerics, while the "chr" and "fct" types are considered text strings.

```{r Initial Mean Calculation}
#First calc, no transformation:
mean(pull(prob2_df, "num_sample"))
mean(pull(prob2_df, "log_vec"))
mean(pull(prob2_df, "char_vec"))
mean(pull(prob2_df, "factor_vec"))

```

```{r Failed Numeric Variable Transformation, eval = FALSE}
#This code did NOT work and created an error message described below, eval = false
char_vec_new = as.numeric(prob2_df, "char_vec")
factor_vec_new = as.numeric(prob2_df, "factor_vec")

mean(pull(prob2_df, "log_vec_new"))
mean(pull(prob2_df, "char_vec_new"))
mean(pull(prob2_df, "factor_vec_new"))
```

When attempting to coerce these other vector types into numerical form, using the `as.numeric` function and attempting to calculate the mean, we receive the error:

`Quitting from lines 95-102 [Numeric Variable Transformation] (p8015_hw1_agd2159.Rmd)
Error:
! 'list' object cannot be coerced to type 'double'
Execution halted`

This indicates that string items in a dataframe cannot be forced into being converted into a particular numerical value. If these datapoints were written numbers but in the character or factor format, then it is my understanding that `as.numeric` could convert them to dbl format for mean calculation.
